---
title: "Automated Web Data Collection"
subtitle: "Day 2"
author:
  - name: "Cornelius Erfort"
    affiliation: "Witten/Herdecke University"
date: "2026-04-25"
format: 
  revealjs:
     css: slides/custom.css
     slide-number: true
     show-slide-number: all
     preview-links: auto
     theme: default
pdf: default
date-format: long
from: markdown+emoji
editor: visual
---

## Recap of Day 1

- **HTML and Web Structure**:
  - Understanding HTML and CSS.
  - Learning how to extract data from web pages using CSS selectorss.
  - Using `rvest` to scrape static web pages effectively.

## Recap of Day 1


- **Web Scraping Techniques**:
  - Introduction to web scraping and its applications.
  - Practical exercises on scraping data from multiple pages using loops.
  - Techniques for handling pagination URLs.

## Recap of Day 1


- **APIs and Data Formats**:
  - Understanding the role of APIs in data retrieval.
  - Learning to work with JSON and other data formats.
  - Using R to interact with APIs and parse JSON data.

------------------------------------------------------------------------

```{r install, echo = F}
# install.packages("rmarkdown")
# install.packages("tidyverse")
# install.packages("qrcode")

library(tidyverse)
library(rmarkdown)
library(qrcode)
library(rvest)
library(xml2)
```

## About today

1.  Dynamic content: when `rvest` is not enough
2.  Live browser scraping with `rvest` (Chromote)
3.  Practical scraping ops: files, logging, and scheduling
4.  Common challenges: CAPTCHAs, rate limits, proxies
5.  Ethics and legal practice
6.  Applied exercises

------------------------------------------------------------------------

## Dynamic Content on Websites

-   Many websites use JavaScript to load data after the initial HTML is loaded
-   Standard tools like `rvest` only see the initial HTML
-   Data may be loaded via AJAX, appear after clicks, or require scrolling

Example (dynamic loading): <https://www.cducsu.de/presse>

------------------------------------------------------------------------

## rvest: `read_html_live()` via Chromote

-   `read_html_live()` runs a real Chrome browser in the background (via `chromote`)
-   Lets you scrape **JavaScript-generated** HTML that `read_html()` can’t see
-   Supports light interaction: click, type, scroll (via the `LiveHTML` object)



------------------------------------------------------------------------

## Basic workflow: `read_html_live()`

```{r echo=T,eval=FALSE, read-html-live-basic}
library(rvest)
library(dplyr)

# Start a live Chrome session and load the page
live <- read_html_live("https://www.cducsu.de/presse")

# Handle cookie banner (Klaro): click “Alle Cookies akzeptieren”
live$click("button.cm-btn.cm-btn-success")

# Click "Mehr laden" (load more items)
live$scroll_into_view("a.button[rel='next']")
live$click("a.button[rel='next']", n_clicks = 2)

# Extract press releases currently visible
items <- live |>
  html_elements(".press-release-teasers [data-drupal-views-infinite-scroll-content-wrapper] article")

out <- tibble(
  title  = items |> html_element("a") |> html_text2(),
  url    = items |> html_element("a") |> html_attr("href") |> paste0("https://www.cducsu.de", .),
  date   = items |> html_element("time") |> html_text2(),
  author = items |> html_element(".truncate") |> html_text2()
)

out |> slice_head(n = 10)
```

------------------------------------------------------------------------

## Inspecting network activity

-   Use browser dev tools to inspect network requests
-   Often you can recreate browser behavior with `httr` once you find the underlying JSON endpoint
-   Example: Find the JSON endpoint behind a table or chart
-   Key idea: the same **CSS selector logic** you use for `html_elements()` is what you use for interactions like `live$click()` / `live$type()`
-   Cursor tip: Chrome DevTools MCP (connect Cursor ↔ DevTools): <https://cursor.com/docs/cli/mcp> and <https://github.com/mcp/chromedevtools/chrome-devtools-mcp>

------------------------------------------------------------------------

## HTTP requests and the httr package

-   Many websites and APIs require you to send HTTP requests directly
-   `httr` is an R package for working with HTTP (GET, POST, PUT, DELETE, etc.)
-   Lets you set headers, send data, handle cookies, and parse responses
-   Useful for simulating browser requests

------------------------------------------------------------------------

## HTTP basics: GET vs. POST

-   **GET**: Retrieve data from a URL (parameters in the URL)
-   **POST**: Send data to a server (parameters in the request body)
-   Many APIs require POST for search, login, or data submission

------------------------------------------------------------------------

## Example: GET request with httr

```{r httr-get, eval=FALSE, echo=T}
library(httr)
# Simple GET request
resp <- GET("https://httpbin.org/get")
content(resp)

# GET with query parameters
resp <- GET("https://httpbin.org/get", query = list(name = "dynamics", course = "webscraping"))
content(resp)
```

------------------------------------------------------------------------

## GET requests and query parameters

-   Query parameters are added to a URL after a `?`

-   Each parameter is a key-value pair: `key=value`

-   Multiple parameters are separated by `&`

-   Example:

    `https://api.example.com/search?query=webscraping&lang=en&page=2`

    -   `query=webscraping` (search term)
    -   `lang=en` (language)
    -   `page=2` (page number)

------------------------------------------------------------------------

## Inspecting HTTP Responses

-   After making a request with `httr`, always check the response:
    -   **Status code:** Was the request successful?
    -   **Content:** What data did you get back?
    -   **Headers:** What metadata did the server send?

```{r httr-inspect, eval=FALSE, echo=TRUE}
resp <- GET("https://httpbin.org/get")

# Check the status code (200 = OK)
status_code(resp)

# See the content (parsed automatically if possible)
content(resp)

# View response headers
headers(resp)
```

------------------------------------------------------------------------

## Example: POST request to a real website

-   Here's how you might send a POST request to [Les Républicains - Actualités](https://republicains.fr/actualites/):

```{r httr-post-republicains, eval=FALSE, echo=TRUE}
library(httr)
# Example POST request (replace body with actual parameters if needed)
resp <- POST(
  "https://republicains.fr/actualites/",
  body = list(param1 = "value1", param2 = "value2"),
  encode = "form"
)
content(resp)
```

<https://republicains.fr/actualites/>

------------------------------------------------------------------------

## Custom headers, authentication, and cookies

-   Some sites require custom headers (e.g., User-Agent, Referer)
-   Use `add_headers()` to set them
-   Handle cookies with `set_cookies()`
-   Use `authenticate()` for basic HTTP authentication

```{r httr-headers, eval=FALSE,echo=T}
# Custom User-Agent
resp <- GET("https://httpbin.org/headers", add_headers(`User-Agent` = "MyScraper/1.0"))
content(resp)

# Cookies
resp <- GET("https://httpbin.org/cookies/set?cookie1=value1", set_cookies(cookie1 = "value1"))
content(resp)
```

------------------------------------------------------------------------

## Working with cookies in httr

-   **Cookies** are small pieces of data stored by the browser to remember your session (e.g., after login)
-   Many sites require cookies to keep you logged in or to track your activity
-   In `httr`, you can set cookies with `set_cookies()` and read cookies from responses
-   To persist cookies across multiple requests, use a `handle`

------------------------------------------------------------------------

## Working with cookies in httr

```{r httr-cookies, eval=FALSE, echo=T}
library(httr)
# Set a cookie in your request
resp <- GET("https://httpbin.org/cookies", set_cookies(mycookie = "cookievalue"))
content(resp)

# Read cookies from a response
cookies <- cookies(resp)
cookies

# Persist cookies across requests using a handle
h <- handle("https://httpbin.org")
GET(handle = h, path = "/cookies/set?cookie1=value1")
GET(handle = h, path = "/cookies")  # cookie1 is sent automatically
```

------------------------------------------------------------------------

## Debugging and inspecting requests

-   Use `verbose()` to see the full request/response
-   Inspect status codes: `status_code(resp)`
-   Check headers: `headers(resp)`

------------------------------------------------------------------------

## When to use `httr` vs. `read_html_live()`

-   Use `httr` for APIs, or simple HTTP requests
-   Use `read_html_live()` when the HTML is built by JavaScript and you need a live browser to see it
-   Often, you can use browser dev tools to find the hidden API and use `httr` instead (faster, more robust)

------------------------------------------------------------------------

## Agent-controlled browsers

-   AI agents can drive a real browser (click/scroll/forms) and can complement `read_html_live()` in exploration workflows
-   Best use: **exploration** (find the right selectors, figure out pagination, discover the underlying XHR/JSON calls)
-   **Tradeoffs:**
    -   Real browser automation → still **slow**
    -   Paid model calls → **costs money**
    -   Not fully deterministic → for research, convert the final approach into a reproducible script (`httr` / `rvest`)


------------------------------------------------------------------------

## Exercise 5: `httr`

-   **Time:** 25-30 minutes
-   **Where in GitHub:** `exercises/05-httr.R`
-   **Goal:** reproduce a browser request with `httr`, inspect the response, and parse the returned content
-   **Steps:**
    1.  Open `exercises/05-httr.R`
    2.  Run a GET request and inspect `status_code()`, `headers()`, and `content()`
    3.  Add query parameters (`GET(..., query = ...)`) for pagination/search

------------------------------------------------------------------------

## Recap: building blocks so far

1.  **Static pages**: `read_html()` + `html_elements()` + `html_text2()` / `html_attr()`
2.  **Dynamic pages**: `read_html_live()` + `live$click()`
3.  **Hidden APIs / backend calls**: use DevTools → reproduce requests with `httr`
4.  **Parse + tidy**: JSON (`jsonlite`) and nested data (`tidyr::unnest_*`)

------------------------------------------------------------------------

## What can go wrong? (1/2)

-   **Selectors break** when the site layout changes
-   **Dynamic content**: element exists only after JS + scrolling + clicks
-   **Rate limits / blocks**: 429s, CAPTCHAs, temporary bans
-   **Session & auth**: cookies/tokens expire, access requires authentication
-   **Data quality issues**: duplicates, missing pages, partial downloads

------------------------------------------------------------------------

## Best practices

-   **Give feedback in your scraping loops:**
    -   Print progress with `print()` or `cat()` or `message()`
-   **Use `tryCatch` to handle errors:**
    -   Prevents your script from stopping if one download fails
    -   Log errors for later review
-   **Save raw HTMLs and log metadata:**
    -   Save each HTML file with a unique name (e.g., based on URL or date)
    -   Keep a log of URLs, download dates, and file paths


------------------------------------------------------------------------

## Helpful tools: Feedback, error handling, and saving data

-   **Example: Robust scraping loop with feedback and logging**

-   This approach helps you:

    -   Track what was downloaded and when
    -   Resume or debug failed downloads
    -   Stay organized as your project grows

    ------------------------------------------------------------------------

## Helpful tools: Feedback, error handling, and saving data

-   **Example: Robust scraping loop with feedback and logging**

-   Use `tryCatch` in R to handle errors and keep your script running

```{r trycatch, eval=FALSE, echo=T}
tryCatch({
  # Your scraping code
}, error = function(e) {
  cat("Error:", e$message, "\n", file = "scrape.log", append = TRUE)
})
```

------------------------------------------------------------------------

## Helpful Functions in R

- **Sys.time()**: Returns the current system time.
- **Sys.Date()**: Returns the current system date.
- **basename()**: Extracts the file name from a file path.
- **dirname()**: Extracts the directory path from a file path.



------------------------------------------------------------------------

## Exercise 7: Helpful tools

-   **Time:** 20-25 minutes
-   **Where in GitHub:** `exercises/06-helpful-tools.R`
-   **Goal:** make your scraper more reliable (progress, caching, logging, error handling)
-   **Steps:**
    1.  Open `exercises/06-helpful-tools.R`
    2.  Add progress output (`cat()`, `message()`) inside a loop
    3.  Add caching (save files to disk and reuse if present)
    4.  Add error handling with `tryCatch()` and write a simple log file

------------------------------------------------------------------------

## Ethics and legal aspects: What you need to know

-   Check the website's terms of service
-   Respect robots.txt `robotstxt`
-   Avoid overloading servers (be `polite`!)
-   GDPR and privacy: Don't collect personal data without consent
-   Copyright: Don't redistribute scraped content without permission
    -   Example (press releases under Creative Commons): <https://www.spdfraktion.de/impressum>
-   Consider adding your contact details in the header
-   When in doubt, ask for permission or use official APIs

------------------------------------------------------------------------

## Example: robots.txt

-   Check `https://example.com/robots.txt` for scraping rules
-   Example: <https://afd.de/robots.txt>
-   Use `robotstxt` R package to check permissions

```{r robotstxt, eval=FALSE,echo=T}
library(robotstxt)
paths_allowed("https://example.com/path")
```

------------------------------------------------------------------------

### Scheduled scraping (local)

-   Use cron jobs (Linux/macOS) or Task Scheduler (Windows) to run R scripts automatically
-   R package: `taskscheduleR` (Windows)
-   Example cron job (run every day at 2am):

```         
0 2 * * * Rscript /path/to/your_script.R
```

------------------------------------------------------------------------

### Scheduling remotely (server / Docker)

-   **Why schedule remotely?**
    -   Your script runs even when your laptop is off
    -   More reliable, scalable, and can run on a schedule 
    -   Useful for long-running or regular scraping tasks
-   **Requirements:**
    -   Access to a remote server (cloud VM, university server, Raspberry Pi, etc.)
    -   Ability to install R and all required packages
    -   (Recommended) Use Docker to package your environment for reproducibility

. . .

-   **Example: Simple Dockerfile for an R scraping script**

``` dockerfile
FROM rocker/r-ver:4.3.1
RUN install2.r --error rvest httr chromote tidyverse
COPY myscript.R /myscript.R
CMD ["Rscript", "/myscript.R"]
```

------------------------------------------------------------------------

## Scraping challenges: CAPTCHAs, rate limits, sessions, proxies

-   CAPTCHAs: Hard to bypass, look for alternative data sources or APIs
-   Rate limits: Add `Sys.sleep()` between requests, randomize intervals
-   Session IDs: Use cookies/headers (`httr`) or keep a live browser session (`read_html_live()`)
-   Proxies: Use proxy servers to rotate IPs (see `httr::use_proxy()`)

------------------------------------------------------------------------

## Using AI assistants for web scraping

-   **How LLMs can help:**
    -   Generate R code for scraping (`rvest`, `httr`, etc.)
    -   Suggest CSS selectors or regular expressions for extracting data
    -   Explain error messages and help debug code
    -   Summarize, clean, or transform scraped data
    -   Brainstorm strategies for scraping tricky or dynamic sites
    -   Provide documentation links and learning resources

------------------------------------------------------------------------

## Using AI assistants for web scraping 

-   **Limitations and challenges:**
    -   May suggest code that doesn't work or is outdated ("hallucination")
    -   Can produce brittle selectors or miss hidden API requests if you don’t check DevTools/Network
-   **Best practices:**
    -   Always test and review generated code before running
    -   Be critical, it might only look like it works
    -   Combine LLM suggestions with browser dev tools and official documentation
    -   Ask for explanations, not just code

------------------------------------------------------------------------

## Automated browser vs script

-   **Small-scale / exploratory tasks:** 
    -   Let the agent control the browser, inspect the DOM/Network, click through flows etc.
    -   Ideal when you need to collect a small sample, test feasibility, or understand page behavior
-   **Larger-scale / production tasks:** move to a script
    -   Browser-driven agent loops become slower and more expensive at scale
    -   Better to convert the discovered logic into an R script

------------------------------------------------------------------------

## What is a “skill” (for an agent)?

-   A **skill** is a reusable set of instructions and conventions you give an assistant so it behaves consistently across tasks.
-   Skills are most useful when tasks are repetitive, high-stakes, or easy to do “almost right”.
-   Example skill (this repo): <https://github.com/cornelius-erfort/automated-web-data-collection-2026/blob/main/.cursor/skills/web-scraper/SKILL.md>

------------------------------------------------------------------------

## Why a web scraping skill is useful

-   Makes results more reliable: e.g. always check `robots.txt`, rate limits, and data provenance.
-   Makes code more consistent: folder structure, naming, logging, retries, and saving outputs.

Example skill checklist:

-   Start with the **simplest** method: API/JSON backend → static HTML → browser automation.
-   Always capture: **URL(s)**, **timestamp**, **request parameters**, and **raw response** (sample).
-   Add: polite delays, error handling, and resumable scraping (save intermediate results).

------------------------------------------------------------------------

## Web scraping skill: Phase 1

The `web-scraper` skill uses a two-phase workflow. **Always do Phase 1 before Phase 2.**

**Phase 1 — Discovery priority ladder** (work top-down; stop at first level that works):

1.  Public / undocumented REST API — check XHR/fetch in DevTools, especially on pagination or filter clicks
2.  GraphQL endpoint — look for `/graphql`, `/gql`
3.  Server-rendered JSON blobs — `__NEXT_DATA__`, `__NUXT__`, `window.__INITIAL_STATE__`, Remix `__remixContext`
4.  React Server Components — Next.js App Router: look for `?_rsc=` requests
5.  CMS/platform APIs — WordPress (`/wp-json/wp/v2/`), Shopify, Drupal JSON:API, Contentful, Ghost
6.  Structured data in HTML — `<script type="application/ld+json">`, microdata, RDFa
7.  `data-` attributes — `data-product-id`, `data-price`, `data-sku`
8.  Stable CSS selectors — semantic HTML (`<article>`, `<time>`, `<table>`); avoid framework-generated classes like `.css-1a2b3c` or `.MuiButton-root`

Output: short report describing what was found and why it's the recommended source.

------------------------------------------------------------------------

## Web scraping skill: Phase 2

**Phase 2 — Script generation** (single file runnable on a schedule):

-   Tooling preference: `httr` / `httpx` (pure HTTP) > headless browser; `curl_cffi` as middle ground; `read_html_live()` / Playwright as last resort
-   Script requirements: CLI args (`--output`, `--format`, `--date-range`, `--page-limit`, optional `--connection`), auto-pagination, polite delays, progress to stderr, exit codes (`0/1/2`), `USER_AGENT` + `HEADERS` at top, single-file script

------------------------------------------------------------------------

## MCP (Model Context Protocol)

-   MCP lets an assistant use **tools** beyond text generation (e.g., browser automation, network inspection, files, databases).
-   It’s best thought of as: **plugins with a typed API** that provide controlled access to capabilities.
-   For web scraping, MCP can help with:
    -   **Browser inspection** (DOM snapshots, clicking through pagination)
    -   **Network requests** (discover hidden JSON endpoints and pagination parameters)


------------------------------------------------------------------------

## Outlook: What else?

-   OCR: Extract text from images and PDFs (`tesseract`, `pdftools`)
-   Regular expressions: Clean and extract data from messy text
-   Text as data
-   Images as data: Download and analyze images
-   Geocoding: Convert addresses to coordinates (`tidygeocoder`)
-   Crawling: `firecrawl`, `crawlR`

------------------------------------------------------------------------

## Exercise 7: Applied Exercise

-   **Time:** 45-60 minutes
-   **Where in GitHub:** `exercises/07-hands-on-project.R`
-   **Goal:** design and implement a minimal end-to-end collection pipeline for a site of your choice
-   **Steps:**
    1.  Pick a topic from the list (or propose your own)
    2.  Before coding: write down the steps (source type? HTML vs `read_html_live()` vs hidden API)
    3.  Build a minimal working version for **one** page/request
    4.  Scale up (pagination / “load more” / looping) and save raw data
    5.  Add reliability features (rate limiting, caching, logging, `tryCatch`)
    6.  Compare with a neighbor and sanity-check the resulting dataset


------------------------------------------------------------------------


## Web Scraping Ideas: Easy

-   [Wikipedia](https://en.wikipedia.org/wiki/List_of_political_scientists) (useful for networks etc.)
-   [Parties' press releases](https://www.spd.de/presse/pressemitteilungen/) (Some parties are very difficult)
-   [Polls (wahlrecht.de)](https://www.wahlrecht.de/umfragen/)
-   [Conference programs (EPSA, DVPW)](https://epsaweb.org/annual-conference/)
-   [Abgeordnetenwatch.de (questions and answers from candidates)](https://www.abgeordnetenwatch.de/)
-   [German Lobby Register](https://www.lobbyregister.bundestag.de/) (can get very complex)
-   [Web Search Results (DuckDuckGo)](https://duckduckgo.com/)
-   [News articles](https://www.nytimes.com/section/world)

------------------------------------------------------------------------

## Web Scraping Ideas: Medium

-   [Korean election results (backend, JSON)](https://info.nec.go.kr/)
-   [Parliamentary protocols (sometimes as documents or PDFs)](https://www.bundestag.de/protokolle)
-   [US live election data from the New York Times (JSON backend)](https://www.nytimes.com/interactive/2020/11/03/us/elections/results-president.html)
-   [Polls (Politico JSON)](https://www.politico.com/interactives/2024/president-election-polls/)
-   [Doctolib appointment availability (JSON)](https://www.doctolib.de/)
-   [ZEIT “NSDAP Mitgliederkartei” name search (hidden API behind search results)](https://www.zeit.de/wissen/2026-04/nsdap-mitgliederkartei-karteikarten-familienmitglieder-suche?freebie=a24c8315)
-   [List of far-right demonstrations from parliamentary query (parsing PDFs and geocoding)](https://dip.bundestag.de/)
-   [Privatization of state owned companies (Treuhand) map](https://treuhandanstalt.online/karte/)

------------------------------------------------------------------------

## Web Scraping Ideas: Difficult

-   German Members of Parliament (MPs) websites (parallel scraping/crawling)
-   [LinkedIn profiles (Python library)](https://pypi.org/project/linkedin-scraper/)
-   [Air quality sensor data worldwide (encrypted via JavaScript)](https://waqi.info/#/c/3.563/8.145/2.2z)
-   [Historic shapefiles for Danish parishes](https://dataforsyningen.dk/data/4840)

------------------------------------------------------------------------

## Goodbye 👋

- Thank you!

